Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-22 main.tex
vector calculus

\begin{proof}
 Let $u \in W^{1,p}(\Omega)$. 
 For each $F \in \calT$ of dimension $n-1$, 
 we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.

 Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

%  We let $T \in \calT$ be the first $n$-simplex. 
%  There exists We already have

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
 Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
 there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{j(m)})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{j(m)})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    .
 \end{align*}
 We summarize the two integrals of $u_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \right)
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
    .
 \end{align*}
 When $1 < p < \infty$, letting $q$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
    \right)^{\frac 1 p}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    .
 \end{align*}
 Recursive application provides the following estimate:
 if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
 such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
 then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(S_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
    \right)
    \| u_{S_0}\|_{L^{p}(S_{0})}
    .
 \end{align*}
 It follows that
 \begin{align*}
    \| w_{m} \|_{L^{p}(S_m)}^{p}
    &\leq 
    (m+1)^{p-1}
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
    \right)
    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{p/q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
    \\&\quad \quad \quad 
    +
    (m+1)^{p-1}
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
    \right)
    \| u_{S_0}\|_{L^{p}(S_{0})}^{p}
    .
 \end{align*}
 Notice that $p/q = p - 1$.
\end{proof}

@@

\section{Extension operator on finite element stars}\label{section:extension}

@@

>>>>

\begin{proof}
 Let $u \in W^{1,p}(\Omega)$. 
 For each $F \in \calT$ of dimension $n-1$, 
 we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F,p} \| \nabla u_F \|_{L^{p}(U_F)}$.

 There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
 \[
    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{P}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
 \]
 In particular, $c_{\star} := u - w_0$ is a constant function. 
 Now, let $T \in \calT$ be any $n$-simplex. 
 By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
 For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{j(m)}$ be a face of dimension $n-1$. 
 We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated \textbf{domain}. % TODO: technical stuff

%  Since $\calT$ is strongly connected, there exists an enumersation of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
 such that $c_{\star} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
 Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
 Since $\nabla u_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}}$,
 there exists a constant $c_{m} := w_{m-1|T_{{m-1}}} - u_{F_{m}|T_{{m-1}}}$.
 We define $w'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla w'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ 
 and 
 $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
 But that already implies $w'_{F_m} = u_{|F_m} - c_{\star}$. 
 We define a measurable function $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$.
 We have $c_{\star} = w_{m} - u_{|\Omega_{m}}$.

 We assess the norm of this potential. We observe 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{{m-1}})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{{m-1}})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 We summarize the two integrals of $u_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
    \right)
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
    .
 \end{align*}
 When $1 < p < \infty$, letting $q$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
    \right)^{\frac 1 p}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 Recursive application provides the following estimate:
 if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
 such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
 then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(S_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
    \right)
    \| u_{S_0}\|_{L^{p}(S_{0})}
    .
 \end{align*}
 It follows that
 \begin{align*}
    \| w_{m} \|_{L^{p}(S_m)}^{p}
    &\leq 
    (m+1)^{p-1}
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
    \right)
    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{p/q}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
    \\&\quad \quad \quad 
    +
    (m+1)^{p-1}
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
    \right)
    \| u_{S_0}\|_{L^{p}(S_{0})}^{p}
    .
 \end{align*}
 Notice that $p/q = p - 1$.

 Repeating this argument produces $w \in L^{p}(\Omega)$ 
 such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{\star}$.
 In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
\end{proof}

@@

\section{Extension operator on finite element stars}\label{section:extension}
% Only define the geometric mapping and its important quantities
% Leave the function spaces etc. for later

@@

Recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^n$ for vector-valued functions with each component in $L^{p}(\Omega)$.

In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    W^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    W^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
More generally, ...
\\

We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $U,V \subset \mathbb{R}^3$ are open sets and suppose that $\phi: U \to V$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(V) \to L^{p}(U)$,
$\phi^{\curl}: \bfL^{p}(V) \to \bfL^{p}(U)$, 
and
$\phi^{\divergence}: \bfL^{p}(V) \to \bfL^{p}(U)$. 
and
$\phi^{\rm b}: L^{p}(V) \to L^{p}(U)$. 
They are defined by % TODO: change inverse convention from here on 
\begin{equation}\label{eq_definition_piola}
\begin{aligned}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{aligned}
\end{equation}
where $v \in L^{p}(V)$ and $\bfw \in \bfL^{p}(V)$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$
These mappings are invertible. 
%
% trace properties 
%
The commutativity properties
\begin{equation}\label{eq_piola_commute}
\begin{aligned}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{aligned}
\end{equation}
for $v \in W^{p}(\grad,U)$, $\bfv \in W^{p}(\curl,U)$, and $\bfw \in W^{p}(\divergence,U)$.  
%

\subsection{Exterior Algebra}

In mathematics, Euclidean space, denoted \(\mathbb{R}^n\), is a fundamental concept representing the \(n\)-dimensional generalization of the familiar 2D and 3D spaces. Multilinear forms are scalar-valued functions that take multiple vectors as input and return a scalar and which are linear in each argument. This leads us to the study of alternating algebra, which focuses on antisymmetric multilinear forms.
Alternating algebra plays a crucial role in various areas of mathematics, including geometry and physics.
\\

Let $V$ be a real vector space. 
Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
if 
\[ 
    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
    = 
    \text{sign}(\pi) 
    u( v_1, v_2, \ldots, v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.

The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) altand \( u_2 \in \Alt^{l}(V) \), their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
defined by the formula 
\[
    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
    = 
    \frac{1}{k! l!} 
    \sum_{ \sigma \in S_{p+q}} 
    \mathrm{sgn}(\sigma) 
    u_1( v_{\sigma(  1)}, \ldots, v_{\sigma(k  )} ) 
    u_2( v_{\sigma(k+1)}, \ldots, v_{\sigma(k+l)} ),
\]
for any \( v_1, v_2, \ldots, v_{p+q} \in V \).
Here, \( S_{p+q} \) denotes the symmetric group on \( p+q \) elements, \( \mathrm{sgn}(\sigma) \) is the sign of the permutation \( \sigma \). The exterior product is bilinear and associative, and satisfies 
\begin{align*}
    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
    \quad 
    u_1 \in \Alt^{k}(V),
    \quad 
    u_2 \in \Alt^{l}(V).
\end{align*}
We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
Moreover, this particular setting comes with a canonical basis. 
We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^n\}\) be the canonical basis dual to the standard unit vectors.
This is a basis of $\Alt^{1}(\bbR^{n})$. 
The set 
\begin{align*}
    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n), % TODO: define sigma 
\end{align*}
is the canonical basis of $\Alt^{k}(\bbR^{n})$. Note that 
\begin{align*}
    \dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}. 
\end{align*}
In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).

We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
The exterior derivative \( d \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
to a \((k+1)\)-form \( d\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
\[
    \omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \omega_{\sigma} \, 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
\]
where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
The exterior derivative \( d\omega \) is defined by
\[
    d\omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \sum_{j=1}^{n} 
    \frac{\partial \omega_{\sigma}}{\partial x^j} 
    \, \cartanx^j \wedge 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
\]
The exterior derivative is linear and nilpotent, which means 
\( d(d\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
Moreover, it satisfies the Leibniz rule:
\[ 
    d(\omega \wedge \eta) 
    = 
    d\omega \wedge \eta + (-1)^{k} \omega \wedge d\eta, 
    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
\]
These properties ensure that the exterior derivative is a crucial tool in differential geometry and calculus on manifolds.

\begin{remark}
    In three dimensions, 
    the calculus of differential forms can be translted into classical vector calculus. 
    This is expressed formally as the commuting diagram 
    \[
    \begin{CD}
        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) @>{d}>> C^\infty\Alt^3(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        @VV{\varpi^{3}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
    \end{CD}
    \]
    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
    \begin{align*}
     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
     = 
     \left( u_1, u_2, u_3 \right), 
     \quad 
     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
     = 
     \left( u_{23}, - u_{13}, u_{12} \right).
     .
    \end{align*}
    In two dimensions, 
    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
    To the authors' best knowledge, neither convention is dominant in the literature.
    On the one hand, we have a commuting diagram 
    \[
    \begin{CD}
        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) 
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        \\
        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
    \end{CD}
    \]
    where the the middle vertical arrow is the isomorphism that satisfies 
    \begin{align*}
        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
        =
        \left( u_1, u_2 \right),
    \end{align*}
    and the other vertical arrows are the identity. 
    Alternatively, we may use the commuting diagram 
    \[
    \begin{CD}
        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega)
        \\
        @VV{\varpi^{0}}V 
        @VV{\varpi^{1}}V 
        @VV{\varpi^{2}}V 
        \\
        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
    \end{CD}
    \]
    where the the middle vertical arrow is the isomorphism that satisfies 
    \begin{align*}
        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
        =
        \left( u_2, -u_1 \right),
    \end{align*}
    and the other vertical arrows are the identity. 
    The utility of exterior calculus is that the doperators of vector calculus can be translated into a common framework that does not depend on the dimension.
\end{remark}

In physics, alternating algebra is crucial in the formulation of theories such as electromagnetism and general relativity. For example, in electromagnetism, the electromagnetic field tensor is an alternating 2-form, and its properties are naturally described using the language of exterior algebra.

- Spivak, Michael. *Calculus on Manifolds*. W. A. Benjamin, 1965.
- Lee, John M. *Introduction to Smooth Manifolds*. Springer, 2012.
- Greub, Werner H. *Multilinear Algebra*. Springer, 1978.
- Bott, Raoul, and Loring W. Tu. *Differential Forms in Algebraic Topology*. Springer, 1982.

These references provide a deeper understanding of the concepts discussed and offer additional insights into the applications and further study of alternating algebra.
